Empirical Check of Machine Homogeneity on Timing Protocol

### 2017-02-13 pt_characterization/machine_cons_check/paper.tex
Add some plots for machine homogeneity check

\begin{document}
\title{Machine Homogeneity Check on EMPv5}

@@

\section{Experiment Notes}
%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8} &  INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb9} &  INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb10} & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb12} & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes}}
\end{table}

The following sections presents experimental results on a machine basis. 
We used four nodes in a cluster. 
Each section exhibits histograms of elapsed time (ET) and process time (PT) 
over increasing INC's task lengths on each individual machine.

%\begin{table}[h]
%\begin{center}
%\begin{tabular}{|l|l|l|l}|} \hline
%Machine & {\tt sodb8} & {\tt sodb9} & {\tt sodb10} & {\tt sodb12} \\ \hline
%1  & \\ \hline
%2  & \\ \hline
%4  & \\ \hline
%8  & \\ \hline
%16 & \\ \hline
%32 & \\ \hline
%64 & \\ \hline
%128 & \\ \hline
%\end{tabular}
%\end{center}
%\caption{Machine-wise Run Statistics: Standard Deviation\label{tab:std_machine}}
%\end{table}

@@

>>>>

\begin{document}
\title{Empirical Check of Machine Homogeneity on Timing Protocol}

@@

\section{Description}
In this work we do a check to see if the result on the same experiment is different 
on different nodes, each with the same machine specification.

\section{Experiment Notes}
We provide a short description of our experimental runs. 
In these experiments we used four nodes ({\tt sodb8}, {\tt sodb9}, {\tt sodb10}, and {\tt sodb12} ) 
in the same cluster.

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8} &  INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb9} &  INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb10} & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb12} & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes}}
\end{table}

\paragraph{Measurement Quality Across the SoDB Nodes:} 
Fig.~\ref{fig:machine_comp} shows 
the standard deviation and relative error of 
elapsed time (ET) and process time (PT) on the different SoDB nodes 
as the task length of INC increases.

\begin{figure}[t]
	\centering
	\subfigure[Standard Deviation - ET]{
		\includegraphics[scale=0.6]{overall/machine_et_std.eps}
        \label{fig:pt_std}
    }
    \subfigure[Relative Error - ET]{
        \includegraphics[scale=0.6]{overall/machine_et_re.eps}
        \label{fig:pt_re}
    }
	\subfigure[Standard Deviation - PT]{
		\includegraphics[scale=0.6]{overall/machine_pt_std.eps}
        \label{fig:pt_std}
    }
    \subfigure[Relative Error - PT]{
        \includegraphics[scale=0.6]{overall/machine_pt_re.eps}
        \label{fig:pt_re}
    }
    \caption{Measurement Quality Comparison among Different SoDB Machines}
    \label{fig:machine_comp}
\end{figure}

\newpage

Each of the following sections exhibits histograms of ET and PT 
over increasing INC's task lengths on each individual node.

@@

\newpage

\section{Conclusion}
My recommendation is to avoid {\tt sodb8} and to use the rest of 
the SoDB nodes for the rest of our experiments. Further investigation is 
needed to examine why the experiment results on {\tt sodb8} are different 
than those of the other nodes.
